Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex

\section{Experiments and Results}
\begin{figure*}[ht!]
  \centering
  \input{figure/sentences.tikz}
  \caption{\small Example Parses: The blue upper edges show CoNLL dependency parses; the red lower edges show oriented link grammar parses. Vertical edges are those with parent 0.  See Appendix~\ref{app:parses} for formatting details and more examples.}
  \label{fig:parses}
\end{figure*}

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJE{update in final version}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, !!! of !!! link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = !!!$ of !!! link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences and !!! of the Russian sentences had at least one multiheaded word.
\noteJE{2 significant digits is enough}

\noteJE{fill these numbers in}

\subsection{Stability of Results}\label{sec:stability}
\begin{figure}[ht!]
  \small
  \centering
  \includegraphics[width=\linewidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Convergence to the direction mapping obtained on the largest run.  Precision relative to that run is very high even for small datasets.  Recall grows as more link types are seen.}\label{fig:convergence}
\end{figure}

>>>>

\section{Experiments and Results}
\begin{figure*}[ht!]
  \vspace{-6pt}
  \centering
  \input{figure/sentences.tikz}
  \caption{\small Example Parses: The blue upper edges show CoNLL dependency parses; the red lower edges show oriented link grammar parses. Vertical edges are those with parent 0.  See Appendix~\ref{app:parses} for formatting details and more examples.}
  \label{fig:parses}
  \vspace{-6pt}
\end{figure*}

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences and 0.15\% of the Russian sentences had at least one multiheaded word.
\noteJE{2 significant digits is enough}
\noteJE{update these numbers}

\subsection{Stability of Results}\label{sec:stability}
\begin{figure}[ht!]
  \small
  \centering
  \includegraphics[width=\linewidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Convergence to the direction mapping obtained on the largest run.  Precision relative to that run is very high even for small datasets.  Recall grows as more link types are seen.}\label{fig:convergence}
\vspace{-6pt}
\end{figure}
